### 2025-09-23 basic-statistics.qmd
20250923 - clarifications

- [effect size](#sec-practicalSignificance)
- [sample size](#sec-sampleVsPopulation)
- [alpha level](#sec-statisticalSignificance)

Knowing any three of the following, you can calculate the fourth: statistical power, [effect size](#sec-practicalSignificance), [sample size](#sec-sampleVsPopulation), and [alpha level](#sec-statisticalSignificance).
Below is `R` code for calculating power for each of various statistical tests (i.e., a *power analysis*).
We use the `pwr` [@R-pwr] and `pwrss` [@R-pwrss] packages to estimate statistical power.
For free point-and-click software for calculating statistical power, see G\*Power: <https://www.psychologie.hhu.de/arbeitsgruppen/allgemeine-psychologie-und-arbeitspsychologie/gpower.html>

>>>>

- [effect size](#sec-practicalSignificance)
- [sample size](#sec-sampleVsPopulation)
- [alpha level](#sec-statisticalSignificance) (Type I error rate)

Knowing any three of the following, you can calculate the fourth (assuming the assumptions of the statistical test are met): statistical power, [effect size](#sec-practicalSignificance), [sample size](#sec-sampleVsPopulation), and [alpha level](#sec-statisticalSignificance) (Type I error rate).
Below is `R` code for calculating power for each of various statistical tests (i.e., a *power analysis*).
We use the `pwr` [@R-pwr] and `pwrss` [@R-pwrss] packages to estimate statistical power.
For free point-and-click software for calculating statistical power, see G\*Power: <https://www.psychologie.hhu.de/arbeitsgruppen/allgemeine-psychologie-und-arbeitspsychologie/gpower.html>
